A Global Market for Marine Conservation

### 2021-02-18 draft.Rmd
Updating draft

---
title: "A Global Market for Marine Conservation"
subtitle: "Draft"
author:
  - "Juan Carlos Villaseñor-Derbez"
  - "Darcy Bradley"
  - "Christopher Costello"
  - "Juan Mayorga"
  - "Andrew Plantinga"
date: "Prepared on `r format(Sys.time(), '%B %d, %Y')`"
abstract: "Humanity depends on the ocean for livelihood, subsitance, and way of life. Yet, many of our activities continiously pose a threat to marine populations and ecosystems. The implementation of Marine Protected Areas (MPAs), where extractive activities are regulated or prohibited on the basis of spatial deliniations, are one of many ways to manage the oceans. Current intenrational agreements call to achieve a certain amount of within-country conservation. Here we explore the benefits from implementing a market for conservation in which nations trade conservation towards a global target. We find that such a market reduces the costs of conservation by 46%, relative to a BAU scenario without a market where each country protects a fixed portion of their waters. When creating 12 distinct markets based on biogeography regionalization, we find that costs are reduced by 34.8%."
fontsize: 12pt
output:
  bookdown::pdf_document2:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: no
header-includes:
  - \usepackage{multirow}
  - \usepackage{float}
  - \usepackage{pdfpages}
  - \usepackage{placeins}
---

@@

@@

\input{results/tab/rlm_trading_prices.tex}

\input{results/tab/rlm_gains_from_trade.tex}

>>>>

---
title: "A Global Market for Marine Conservation"
subtitle: "Draft"
# https://stackoverflow.com/questions/52918716/authors-and-affiliations-in-the-yaml-of-rmarkdown
author:
  - Juan Carlos Villaseñor-Derbez:
      email: juancarlos@ucsb.edu
      institute: bren
      correspondence: true
  - name: Darcy Bradley
    institute: bren
  - name: Christopher Costello
    institute: bren
  - name: Juan Mayorga
    institute: bren
  - name: Andrew Plantinga
    institute: bren
institute:
  - bren: Bren School of Environmental Science and Management, University of California Santa Barbara
date: "Prepared on `r format(Sys.time(), '%B %d, %Y')`"
abstract: "Humanity depends on the ocean for livelihood, subsitance, and way of life. Yet, many of our activities continiously pose a threat to marine populations and ecosystems. The implementation of Marine Protected Areas (MPAs), where extractive activities are regulated or prohibited on the basis of spatial deliniations, are one of many ways to manage the oceans. Current intenrational agreements call to achieve a certain amount of within-country conservation. Here we explore the benefits from implementing a market for conservation in which nations trade conservation towards a global target. We find that such a market reduces the costs of conservation by 46%, relative to a BAU scenario without a market where each country protects a fixed portion of their waters. When creating 12 distinct markets based on biogeography regionalization, we find that costs are reduced by 34.8%."
fontsize: 12pt
output:
  bookdown::pdf_document2:
    citation_package: natbib
    fig_caption: yes
    number_sections: yes
    toc: no
    pandoc_args:
      - '--lua-filter=scholarly-metadata.lua'
      - '--lua-filter=author-info-blocks.lua'
header-includes:
  - \usepackage{multirow}
  - \usepackage{float}
  - \usepackage{pdfpages}
  - \usepackage{placeins}
---

@@

# Important sentences

Importantly, the quality of a patch can be defined independently of other pixels. This is true for habitat suitability, in which the abiotic characteristics that determine the suitability of a patch are independent of the protected status of any patch.

@@

\input{results/tab/trading_prices_rlm.tex}

\input{results/tab/gains_from_trade_rlm.tex}
